---
title: "Unit-4"
author: "D Jyothi"
date: "2024-07-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Generating Random Numbers 
```{r}
sample(1:10, 2)
```

# Each run generates different results:
```{r}
sample(1:10, 2); sample(1:10, 2)
```

# To get the same result each time, set the seed to a
# number of your choice:
```{r}
set.seed(314); sample(1:10, 2)
set.seed(314); sample(1:10, 2)
```
#normal distribution it is called rnorm. 

```{r}
rnorm(10, 2, 1)     # Normal distribution 
qnorm(0.9, 2, 1)    # Upper 90 % quantile of distribution
dnorm(2.5, 2, 1)    # Density function f(2.5)
pnorm(2.5, 2, 1)    # Cumulative distribution function F(2.5)
```
# Summarizing data 
```{r}
vec <- c(1, 2, 3, 4, 5)
summary(vec)
```
#summarizing factor 
```{r}
vec <- factor(c("apple", "banana", "apple", "orange", "banana", "apple"))
summary(vec)
```
#Summarizing character vector 
```{r}
vec <- c("apple", "banana", "apple", "orange", "banana", "apple")
summary(vec)
```
#summarizing a character vector 
```{r}
vec <- c(TRUE, FALSE, TRUE, NA, FALSE, TRUE)
summary(vec)
```
#summarizing a complex number
```{r}
vec <- c(1+2i, 3-4i, 5+6i)
summary(vec)
```
#summarizing a date 
```{r}
vec <- as.Date(c("2022-01-01", "2022-06-15", "2022-12-31"))
summary(vec)
```
#Calculating Relative Frequencies 
```{r}
data_frame <- data.frame(
  Category = factor(c("A", "B", "A", "C", "B", "A", "C", "C", "B", "A"))
)
print(data_frame)
absolute_frequency_df <- table(data_frame$Category)
print(absolute_frequency_df)
relative_frequency_df <- absolute_frequency_df / nrow(data_frame)
print(relative_frequency_df)
```
# Contingency Table with Two Factors
```{r}
data <- data.frame(
  Gender = factor(c("Male", "Female", "Female", "Male", "Male", "Female")),
  Preference = factor(c("A", "A", "B", "B", "A", "B"))
)
print(data)
#contingency table
contingency_table <- table(data$Gender, data$Preference)
print(contingency_table)
```
```{r}
# chi-squared test in R
data <- data.frame(
  Gender = factor(c("Male", "Female", "Female", "Male", "Male", "Female", "Male", "Female", "Female", "Male")),
  Preference = factor(c("A", "A", "B", "B", "A", "B", "A", "B", "A", "B"))
)
print(data)
contingency_table <- table(data$Gender, data$Preference)
print(contingency_table)
chi_squared_test <- chisq.test(contingency_table)
print(chi_squared_test)

chi_squared_test <- chisq.test(contingency_table)
print(chi_squared_test)
```
```{r}
#Quartiles
data <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
print(data)
f <- c(0.25,0.50,0.75)
quantile_value <- quantile(data, probs = f)
print(quantile_value)
```
```{r}
#z- Score 
# Create a sample numeric vector
data <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
print(data)
# Calculate the mean of the data
mean_data <- mean(data)
# Calculate the standard deviation of the data
sd_data <- sd(data)
# Print the mean and standard deviation
print(paste("Mean:", mean_data))
print(paste("Standard Deviation:", sd_data))
# Calculate the z-scores
z_scores <- (data - mean_data) / sd_data
# Print the z-scores
print(z_scores)
```
```{r}
# Example 2 on Z-Score 
# Create a sample numeric vector
data <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
# Calculate the z-scores using the scale() function
z_scores <- scale(data)
# Print the z-scores
print(z_scores)
```

#T-test 
# Step 1: Create data vectors
```{r}
group1 <- c(5, 7, 8, 6, 9)
group2 <- c(10, 11, 12, 14, 13)
# Step 2: Perform two-sample t-test
t_test_result <- t.test(group1, group2)

# Step 3: Display the results
print(t_test_result)
```
```{r}

#Testing sample propositions in R
#In City A, 60 out of 150 people prefer electric cars.
#	In City B, 80 out of 200 people prefer electric cars.
```{r}
successes <- c(60, 80)
trials <- c(150, 200)
result <- prop.test(successes, trials)
print(result)
```

# Testing normality in R Programming
```{r}
set.seed(123) # Set seed for reproducibility
sample_data <- rnorm(50, mean = 100, sd = 15)
shapiro_test_result <- shapiro.test(sample_data)
print(shapiro_test_result)
qqnorm(sample_data)
qqline(sample_data, col = "red")
```
```{r}
# comparing means of two samples

group1 <- c(5, 7, 8, 6, 9)
group2 <- c(10, 11, 12, 14, 13)
# Perform two-sample t-test
t_test_result <- t.test(group1, group2)
print(t_test_result)

# Testing correlation for significance

heights <- c(150, 160, 170, 180, 190)
weights <- c(55, 65, 70, 80, 90)

# Perform correlation test
correlation_test_result <- cor.test(heights, weights)

# Display the results
print(correlation_test_result)
```
```{r}
# Linear regression
# Sample data for study hours and exam scores
study_hours <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
exam_scores <- c(55, 62, 70, 75, 80, 85, 88, 92, 94, 96)
data <- data.frame(study_hours = study_hours, exam_scores = exam_scores)
lm_model <- lm(exam_scores ~ study_hours, data = data)
summary(lm_model)
```

# Logistic Regression 
```{r}
study_hours <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
pass_fail <- c(0, 0, 0, 0, 1, 1, 1, 1, 1, 1)
logit_model <- glm(pass_fail ~ study_hours, data = data, family = binomial)
summary(logit_model)
```
# clustering with R.
# Generate synthetic data for annual income and spending score
```{r}
set.seed(123)  # Set seed for reproducibility
income <- rnorm(100, mean = 50, sd = 10)
spending_score <- rnorm(100, mean = 50, sd = 15)

# Combine data into a data frame
mall_data <- data.frame(income = income, spending_score = spending_score)

k <- 3
kmeans_model <- kmeans(mall_data, centers = k, nstart = 20)
print(kmeans_model)
plot(mall_data, col = kmeans_model$cluster)
points(kmeans_model$centers, col = 1:k, pch = 8, cex = 2)

```


















